---
title: "Closing a semester during the COVID-19 pandemic: Higher education professionals seeking and sharing advice on instructional design strategies in Reddit"
author: "K. Bret Staudt Willet, Pauline S. Muljana"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, include=FALSE, eval=TRUE)
library(tidyverse)
library(anytime)
library(lubridate)
library(kableExtra)
library(ggplot2)
library(quanteda)
library(tm)
library(viridis)
library(topicmodels)
library(tidytext)
library(seriation)
library(cowplot)

#devtools::install_github("ropenscilabs/roomba")  # <------ currently returns an error and cannot install
#devtools::install_github("jrosen48/roomba")  # this one works; only have to install once
library(roomba)
```

## Introduction

The purpose of this study is to explore how higher-education professionals used Reddit for professional learning in the midst of the COVID-19 pandemic. We frame this inquiry with a systems thinking perspective.

We seek to answer three research questions. We examine the r/Professors and r/highereducation subreddits at the end of the first semester disrupted by COVID-19 and in preparation for the next.

- RQ1: To what extent, if any, did *individual contributions* in the r/Professors and r/highereducation subreddits change?
- RQ2: To what extent, if any, did *content interactions* in r/Professors and r/highereducation change?
- RQ3: What are the *popular topics* asked and advised in the r/Professors and r/highereducation subreddits?

For the third research question, we categorize the answer into *institutional*, *faculty*, and *student* factors.

## Read in posts

```{r}
date_start19 <- 
  as_datetime("2019-05-01 04:00:00 UTC") %>% 
  ymd_hms() %>%
  with_tz(tzone = "US/Eastern")
date_end19 <- 
  as_datetime("2019-09-01 03:59:59 UTC") %>% 
  ymd_hms() %>%
  with_tz(tzone = "US/Eastern")
date_start20 <- 
  as_datetime("2020-05-01 04:00:00 UTC") %>% 
  ymd_hms() %>%
  with_tz(tzone = "US/Eastern")
date_end20 <- 
  as_datetime("2020-09-01 03:59:59 UTC") %>% 
  ymd_hms() %>%
  with_tz(tzone = "US/Eastern")
```

```{r, message=FALSE}
subreddit_posts_he19 <- 
  read_csv("r-highereducation-posts-2019.csv") %>% 
  mutate(post_date_time = with_tz(post_date_time, tzone = "US/Eastern"),
         year = year(post_date_time)) %>%
    filter(post_date_time >= date_start19,
           post_date_time <= date_end19)
subreddit_posts_he20 <- 
  read_csv("r-highereducation-posts-2020.csv") %>% 
  mutate(post_date_time = with_tz(post_date_time, tzone = "US/Eastern"),
         year = year(post_date_time)) %>%
    filter(post_date_time >= date_start20,
           post_date_time <= date_end20)
subreddit_posts_prof19 <- 
  read_csv("r-Professors-posts-2019.csv") %>% 
  mutate(post_date_time = with_tz(post_date_time, tzone = "US/Eastern"),
         year = year(post_date_time)) %>%
  filter(post_date_time >= date_start19,
         post_date_time <= date_end19)
subreddit_posts_prof20 <- 
  read_csv("r-Professors-posts-2020.csv") %>% 
  mutate(post_date_time = with_tz(post_date_time, tzone = "US/Eastern"),
         year = year(post_date_time)) %>%
  filter(post_date_time >= date_start20,
         post_date_time <= date_end20)
```

## Read in comments

```{r}
comments_end19 <- 
  as_datetime("2019-10-01 03:59:59 UTC") %>% 
  ymd_hms() %>%
  with_tz(tzone = "US/Eastern")
comments_end20 <- 
  as_datetime("2020-10-01 03:59:59 UTC") %>% 
  ymd_hms() %>%
  with_tz(tzone = "US/Eastern")
```

```{r, message=FALSE}
subreddit_comments_he19_thru_sept <- 
  read_csv("r-highereducation-comments-2019.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start19,
         comment_date_time <= comments_end19)
subreddit_comments_he20_thru_sept <- 
  read_csv("r-highereducation-comments-2020.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start20,
         comment_date_time <= comments_end20)
subreddit_comments_prof19_thru_sept <- 
  read_csv("r-Professors-comments-2019.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start19,
         comment_date_time <= comments_end19)
subreddit_comments_prof20_thru_sept <- 
  read_csv("r-Professors-comments-2020.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start20,
         comment_date_time <= comments_end20)

subreddit_comments_he19 <- 
  read_csv("r-highereducation-comments-2019.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start19,
         comment_date_time <= date_end19)
subreddit_comments_he20 <- 
  read_csv("r-highereducation-comments-2020.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start20,
         comment_date_time <= date_end20)
subreddit_comments_prof19 <- 
  read_csv("r-Professors-comments-2019.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start19,
         comment_date_time <= date_end19)
subreddit_comments_prof20 <- 
  read_csv("r-Professors-comments-2020.csv") %>% 
  mutate(comment_date_time = with_tz(comment_date_time, tzone = "US/Eastern"),
         year = year(comment_date_time)) %>%
  filter(comment_date_time >= date_start20,
         comment_date_time <= date_end20)
```

### Table 1. Inidividual Contributions by Subreddit (2019 vs. 2020)

```{r, message=FALSE}
table1_contributions0 <-
  bind_cols(
    c("posts", "posters", "comments", "commenters"),
    c(nrow(subreddit_posts_he19),
      length(unique(subreddit_posts_he19$post_author)),
      nrow(subreddit_comments_he19),
      length(unique(subreddit_comments_he19$comment_author))
    ),
    c(nrow(subreddit_posts_he20),
      length(unique(subreddit_posts_he20$post_author)),
      nrow(subreddit_comments_he20),
      length(unique(subreddit_comments_he20$comment_author))
    ),
    c(nrow(subreddit_posts_prof19),
      length(unique(subreddit_posts_prof19$post_author)),
      nrow(subreddit_comments_prof19),
      length(unique(subreddit_comments_prof19$comment_author))
    ),
    c(nrow(subreddit_posts_prof20),
      length(unique(subreddit_posts_prof20$post_author)),
      nrow(subreddit_comments_prof20),
      length(unique(subreddit_comments_prof20$comment_author))
    )
  )
```

```{r, include=TRUE}
table1_contributions <-
  table1_contributions0 %>%
  knitr::kable(align = 'c',
               row.names = FALSE,
               col.names = c("", "2019", "2020", "2019", "2020")
  ) %>% 
  kableExtra::add_header_above(
    c(" " = 1,
      "r/higheredcuation" = 2, 
      "r/Professors" = 2)
  ) %>%
  kableExtra::kable_styling(c("striped", "bordered"))

table1_contributions
```

```{r, eval=FALSE}
# requires webshot::install_phantomjs()
save_kable(table1_contributions, "output/table1-contributions.png")
```

### Figure 1. Daily Posts and Comments by Subreddit (2019 vs. 2020)

```{r}
he19_posts_table <-
  subreddit_posts_he19 %>%
  pull(post_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/highereducation',
         year = '2019',
         type = 'Posts',
         date = ymd(date))
he20_posts_table <-
  subreddit_posts_he20 %>%
  pull(post_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/highereducation',
         year = '2020',
         type = 'Posts',
         date = ymd(date))
he19_comments_table <-
  subreddit_comments_he19 %>%
  filter(comment_date_time <= date_end19) %>%
  pull(comment_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/highereducation',
         year = '2019',
         type = 'Comments',
         date = ymd(date))
he20_comments_table <-
  subreddit_comments_he20 %>%
  filter(comment_date_time <= date_end20) %>%
  pull(comment_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/highereducation',
         year = '2020',
         type = 'Comments',
         date = ymd(date))

prof19_posts_table <-
  subreddit_posts_prof19 %>%
  pull(post_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/Professors',
         year = '2019',
         type = 'Posts',
         date = ymd(date))
prof20_posts_table <-
  subreddit_posts_prof20 %>%
  pull(post_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/Professors',
         year = '2020',
         type = 'Posts',
         date = ymd(date))
prof19_comments_table <-
  subreddit_comments_prof19 %>%
  filter(comment_date_time <= date_end19) %>%
  pull(comment_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/Professors',
         year = '2019',
         type = 'Comments',
         date = ymd(date))
prof20_comments_table <-
  subreddit_comments_prof20 %>%
  filter(comment_date_time <= date_end20) %>%
  pull(comment_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(subreddit = 'r/Professors',
         year = '2020',
         type = 'Comments',
         date = ymd(date))

to_plot <-
  bind_rows(he19_posts_table, he19_comments_table, 
            prof19_posts_table, prof19_comments_table,
            he20_posts_table, he20_comments_table, 
            prof20_posts_table, prof20_comments_table
  ) %>%
  group_by(year) %>%
  complete(date, nesting(subreddit, type), fill = list(n = 0)) %>%
  ungroup() %>%
  mutate(type = factor(type, levels = c("Posts", "Comments")))
```

```{r, include=TRUE, message=FALSE, fig.width=9, fig.height=9}
ggplot(data = to_plot, 
       mapping = aes(x = date, y = n, color = subreddit)) +
  geom_point(size = 2, alpha=.6) +
  geom_smooth(size = 0.5) +
  facet_grid(cols = vars(year), 
             rows = vars(type),
             scales = 'free') +
  scale_color_manual(values = c("#63ACBE", "#EE442F")) + 
  xlab(NULL) +
  ylab(NULL) +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "gray30"),
        panel.grid.minor = element_line(color = "gray90"),
        axis.title=element_text(size = 24, family = 'serif'),
        axis.text=element_text(size = 14, family = 'serif'),
        strip.text.x = element_text(size = 24, family = 'serif'),
        strip.text.y = element_text(size = 24, family = 'serif'),
        legend.position='bottom',
        legend.box = 'vertical',
        legend.box.background = element_rect(),
        legend.title=element_text(size = 24, family = 'serif'), 
        legend.text=element_text(size = 18, family = 'serif')
  ) +
  labs(color='Subreddit')
```

```{r, eval=FALSE}
ggsave("output/fig1-posts-comments-over-time.png", width = 9, height = 9)
``` 

### Table 2. Content Interactions by Subreddit (2019 vs. 2020)

```{r, message=FALSE}
he19 <-
  subreddit_posts_he19 %>%
  left_join(subreddit_comments_he19_thru_sept, 
            by=c('subreddit', 'post_id', 'year'))
he19_posts_n <-
  he19 %>%
  pull(post_id) %>%
  unique() %>%
  length()
he19_threads_n <-
  he19 %>%
  filter(!is.na(comment_id)) %>%
  distinct(post_id) %>%
  nrow() 
he19_comments_in_threads_n <-
  he19 %>%
  filter(!is.na(comment_id)) %>%
  nrow()
he19_response_rate <-
  round(100 * he19_threads_n / he19_posts_n, 2)
he19_comments_per_thread <-
  he19 %>%
  filter(!is.na(comment_id)) %>%
  group_by(post_id) %>%
  summarize(n_comments = n())
he19_thread_length <-
  he19_comments_per_thread%>%
  summarize(Mean = round(mean(n_comments), 2),
            SD = round(sd(n_comments), 2),
            Median = median(n_comments),
            Max = max(n_comments)
  ) %>%
  unlist(use.names=FALSE)
he19_col <- 
  c(he19_posts_n, he19_threads_n, he19_comments_in_threads_n, he19_response_rate, 
    he19_thread_length
    )

he20 <-
  subreddit_posts_he20 %>%
  left_join(subreddit_comments_he20_thru_sept, 
            by=c('subreddit', 'post_id', 'year'))
he20_posts_n <-
  he20 %>%
  pull(post_id) %>%
  unique() %>%
  length()
he20_threads_n <-
  he20 %>%
  filter(!is.na(comment_id)) %>%
  distinct(post_id) %>%
  nrow() 
he20_comments_in_threads_n <-
  he20 %>%
  filter(!is.na(comment_id)) %>%
  nrow()
he20_response_rate <-
  round(100 * he20_threads_n / he20_posts_n, 2)
he20_comments_per_thread <-
  he20 %>%
  filter(!is.na(comment_id)) %>%
  group_by(post_id) %>%
  summarize(n_comments = n())
he20_thread_length <-
  he20_comments_per_thread%>%
  summarize(Mean = round(mean(n_comments), 2),
            SD = round(sd(n_comments), 2),
            Median = median(n_comments),
            Max = max(n_comments)
  ) %>%
  unlist(use.names=FALSE)
he20_col <- 
  c(he20_posts_n, he20_threads_n, he20_comments_in_threads_n, he20_response_rate, 
    he20_thread_length
    )

prof19 <-
  subreddit_posts_prof19 %>%
  left_join(subreddit_comments_prof19_thru_sept, 
            by=c('subreddit', 'post_id', 'year'))
prof19_posts_n <-
  prof19 %>%
  pull(post_id) %>%
  unique() %>%
  length()
prof19_threads_n <-
  prof19 %>%
  filter(!is.na(comment_id)) %>%
  distinct(post_id) %>%
  nrow() 
prof19_comments_in_threads_n <-
  prof19 %>%
  filter(!is.na(comment_id)) %>%
  nrow()
prof19_response_rate <-
  round(100 * prof19_threads_n / prof19_posts_n, 2)
prof19_comments_per_thread <-
  prof19 %>%
  filter(!is.na(comment_id)) %>%
  group_by(post_id) %>%
  summarize(n_comments = n())
prof19_thread_length <-
  prof19_comments_per_thread%>%
  summarize(Mean = round(mean(n_comments), 2),
            SD = round(sd(n_comments), 2),
            Median = median(n_comments),
            Max = max(n_comments)
  ) %>%
  unlist(use.names=FALSE)
prof19_col <- 
  c(prof19_posts_n, prof19_threads_n, prof19_comments_in_threads_n, 
    prof19_response_rate, prof19_thread_length
    )

prof20 <-
  subreddit_posts_prof20 %>%
  left_join(subreddit_comments_prof20_thru_sept, 
            by=c('subreddit', 'post_id', 'year'))
prof20_posts_n <-
  prof20 %>%
  pull(post_id) %>%
  unique() %>%
  length()
prof20_threads_n <-
  prof20 %>%
  filter(!is.na(comment_id)) %>%
  distinct(post_id) %>%
  nrow() 
prof20_comments_in_threads_n <-
  prof20 %>%
  filter(!is.na(comment_id)) %>%
  nrow()
prof20_response_rate <-
  round(100 * prof20_threads_n / prof20_posts_n, 2)
prof20_comments_per_thread <-
  prof20 %>%
  filter(!is.na(comment_id)) %>%
  group_by(post_id) %>%
  summarize(n_comments = n())
prof20_thread_length <-
  prof20_comments_per_thread%>%
  summarize(Mean = round(mean(n_comments), 2),
            SD = round(sd(n_comments), 2),
            Median = median(n_comments),
            Max = max(n_comments)
  ) %>%
  unlist(use.names=FALSE)
prof20_col <- 
  c(prof20_posts_n, prof20_threads_n, prof20_comments_in_threads_n, 
    prof20_response_rate, prof20_thread_length
    )

table2_content0 <-
  bind_cols(
    c("posts", "threads", "comments in threads", "response rate",
      "mean", "SD", "Median", "Max"),
    he19_col, he20_col, prof19_col, prof20_col
  )
```

```{r, include=TRUE}
table2_content <-
  table2_content0 %>%
  knitr::kable(align = 'c',
               row.names = FALSE,
               col.names = c("", "2019", "2020", "2019", "2020")
  ) %>% 
  kableExtra::add_header_above(
    c(" " = 1,
      "r/higheredcuation" = 2, 
      "r/Professors" = 2)
  ) %>%
  kableExtra::kable_styling(c("striped", "bordered"))

table2_content
```

```{r, eval=FALSE}
# requires webshot::install_phantomjs()
save_kable(table2_content, "output/table2-content-interactions.png")
```

### Word Clouds

```{r}
my_extra_stopwords <-
  c("NA", "removed", "deleted", "just", "can", "like", "also", "even")
```

**r/highereducation**

```{r, message=FALSE}
corpus_posts_he19 <- 
  subreddit_posts_he19 %>%
  mutate(text = paste(post_title, post_text),
         text = tolower(text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = post_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_posts_he19 <- 
  quanteda::dfm(corpus_posts_he19, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)

corpus_posts_he20 <- 
  subreddit_posts_he20 %>%
  mutate(text = paste(post_title, post_text),
         text = tolower(text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = post_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_posts_he20 <- 
  quanteda::dfm(corpus_posts_he20, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)

corpus_comments_he19 <- 
  subreddit_comments_he19 %>%
  mutate(text = tolower(comment_text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = comment_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_comments_he19 <- 
  quanteda::dfm(corpus_comments_he19, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)

corpus_comments_he20 <- 
  subreddit_comments_he20 %>%
  mutate(text = tolower(comment_text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = comment_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_comments_he20 <- 
  quanteda::dfm(corpus_comments_he20, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_posts_he19 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_posts_he20 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_comments_he19 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_comments_he20 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

**r/Professors**

```{r, message=FALSE}
corpus_posts_prof19 <- 
  subreddit_posts_prof19 %>%
  mutate(text = paste(post_title, post_text),
         text = tolower(text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = post_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_posts_prof19 <- 
  quanteda::dfm(corpus_posts_prof19, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)

corpus_posts_prof20 <- 
  subreddit_posts_prof20 %>%
  mutate(text = paste(post_title, post_text),
         text = tolower(text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = post_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_posts_prof20 <- 
  quanteda::dfm(corpus_posts_prof20, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)

corpus_comments_prof19 <- 
  subreddit_comments_prof19 %>%
  mutate(text = tolower(comment_text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = comment_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_comments_prof19 <- 
  quanteda::dfm(corpus_comments_prof19, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)

corpus_comments_prof20 <- 
  subreddit_comments_prof20 %>%
  mutate(text = tolower(comment_text),
         text = tm::removePunctuation(text)
  ) %>%
  rename(doc_id = comment_id) %>%
  select(doc_id, text) %>%
  quanteda::corpus(text_field = 'text')
dfm_comments_prof20 <- 
  quanteda::dfm(corpus_comments_prof20, 
      remove = c(my_extra_stopwords,
                 quanteda::stopwords("english")),
      remove_url = TRUE,
      remove_punct = TRUE,
      remove_symbols = TRUE,
      remove_numbers = TRUE)
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_posts_prof19 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_posts_prof20 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_comments_prof19 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

```{r, include=TRUE, fig.width=9, fig.height=9}
dfm_comments_prof20 %>%
  textplot_wordcloud(min_count = 10, 
                     random_order = FALSE, 
                     rotation = 0.25, 
                     color = viridis_pal()(8)
  )
```

### Figure 2. Topics by Subreddit (2020)

```{r}
find_top_terms <- 
  function(x, year) {
    x[rowSums(x) != 0, ] %>%
      topicmodels::LDA(k = 5, 
                       control = list(seed = 12162020)) %>%
      tidytext::tidy(matrix = "beta") %>%
      filter(term != "im") %>%
      group_by(topic) %>%
      top_n(10, beta) %>%
      ungroup() %>%
      arrange(topic, -beta) %>%
      mutate(topic = str_c(year, "-", topic))
  }

top_terms_posts_he19 <- find_top_terms(dfm_posts_he19, 2019)
top_terms_posts_he20 <- find_top_terms(dfm_posts_he20, 2020)

top_terms_posts_prof19 <- find_top_terms(dfm_posts_prof19, 2019)
top_terms_posts_prof20 <- find_top_terms(dfm_posts_prof20, 2020)

top_terms_comments_he19 <- find_top_terms(dfm_comments_he19, 2019)
top_terms_comments_he20 <- find_top_terms(dfm_comments_he20, 2020)

top_terms_comments_prof19 <- find_top_terms(dfm_comments_prof19, 2019)
top_terms_comments_prof20 <- find_top_terms(dfm_comments_prof20, 2020)
```

```{r}
compare_top_terms <- 
  function(x, y) {
    merged_terms <-
      full_join(x, y, by = c("topic", "term", "beta")) %>%
      complete(topic, term, fill = list(beta = 0))
    
    merged_terms_seriated <-
      merged_terms %>%
      pivot_wider(names_from = topic,
                  values_from = beta) %>%
      column_to_rownames('term') %>%
      as.matrix() %>%
      seriation::seriate()
    
    terms_ordered <-
      unique(merged_terms$term)[seriation::get_order(merged_terms_seriated, dim=1)]
    topics_ordered <-
      unique(merged_terms$topic)[seriation::get_order(merged_terms_seriated, dim=2)]
    
    merged_terms_to_plot <-
      merged_terms %>%
      mutate(
             term = factor(term, levels = terms_ordered),
             year = sub("-[0-9]", "", topic),
             topic = sub("20[0-9][0-9]-", "", topic)
      )
    
    merged_terms_to_plot
  }

top_terms_posts_he_to_plot <- 
  compare_top_terms(top_terms_posts_he19, top_terms_posts_he20)
top_terms_posts_prof_to_plot <- 
  compare_top_terms(top_terms_posts_prof19, top_terms_posts_prof20)

top_terms_comments_he_to_plot <- 
  compare_top_terms(top_terms_comments_he19, top_terms_comments_he20) %>%
  mutate(term = fct_rev(term))
top_terms_comments_prof_to_plot <- 
  compare_top_terms(top_terms_comments_prof19, top_terms_comments_prof20)
```

```{r}
theme_formatting <- 
  theme(plot.title = element_text(size=20, family='serif', hjust = 0.5),
        axis.title = element_text(size=16, family='serif'),
        axis.text = element_text(size=10, family='serif'),
        strip.text.x = element_text(size = 16, family='serif'),
        legend.title = element_text(size=8, family='serif'), 
        legend.text = element_text(size=7, family='serif'),
        legend.position='left',
        legend.background = element_blank(),
        legend.box.background = element_rect(colour='black'),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(color = 'black')
  )
```

```{r, fig.width=4, fig.height=5}
plot_posts_he <- 
  ggplot(top_terms_posts_he_to_plot, aes(x = topic, y = term)) +
  geom_tile(aes(fill = beta), color = 'white', size = 0.2) + 
  scale_fill_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x < .015, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), .015)), 
           1)
  }
  ) +
  facet_wrap(~ year) +
  xlab("Topic") +
  scale_x_discrete(position='bottom') +
  ylab("Term") +
  scale_y_discrete(position='right') +
  theme_bw() +
  labs(fill = "Topic-Word Density") +
  ggtitle("r/highereducation Posts") +
  theme_formatting +
  panel_border()

plot_posts_he
```

```{r, fig.width=4, fig.height=5}
plot_posts_prof <- 
  ggplot(top_terms_posts_prof_to_plot, aes(x = topic, y = term)) +
  geom_tile(aes(fill = beta), color = 'white', size = 0.2) + 
  scale_fill_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x < .015, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), .015)), 
           1)
  }
  ) +
  facet_wrap(~ year) +
  xlab("Topic") +
  scale_x_discrete(position='bottom') +
  ylab("Term") +
  scale_y_discrete(position='right') +
  theme_bw() +
  labs(fill = "Topic-Word Density") +
  ggtitle("r/Professors Posts") +
  theme_formatting +
  panel_border()

plot_posts_prof
```

```{r, fig.width=4, fig.height=5}
plot_comments_he <- 
  ggplot(top_terms_comments_he_to_plot, aes(x = topic, y = term)) +
  geom_tile(aes(fill = beta), color = 'white', size = 0.2) + 
  scale_fill_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x < .015, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), .015)), 
           1)
  }
  ) +
  facet_wrap(~ year) +
  xlab("Topic") +
  scale_x_discrete(position='bottom') +
  ylab("Term") +
  scale_y_discrete(position='right') +
  theme_bw() +
  labs(fill = "Topic-Word Density") +
  ggtitle("r/highereducation Comments") +
  theme_formatting +
  panel_border()

plot_comments_he
```

```{r, fig.width=4, fig.height=5}
plot_comments_prof <- 
  ggplot(top_terms_comments_prof_to_plot, aes(x = topic, y = term)) +
  geom_tile(aes(fill = beta), color = 'white', size = 0.2) + 
  scale_fill_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x < .015, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), .015)), 
           1)
  }
  ) +
  facet_wrap(~ year) +
  xlab("Topic") +
  scale_x_discrete(position='bottom') +
  ylab("Term") +
  scale_y_discrete(position='right') +
  theme_bw() +
  labs(fill = "Topic-Word Density") +
  ggtitle("r/Professors Comments") +
  theme_formatting +
  panel_border()

plot_comments_prof
```

```{r, include=TRUE, message=FALSE, fig.width=8, fig.height=10}
topics_by_subreddit <- 
  cowplot::plot_grid(plot_posts_he, plot_comments_he,
                     plot_posts_prof, plot_comments_prof,
                     nrow = 2
  )

topics_by_subreddit
```

```{r, eval=FALSE}
ggsave("output/fig2-topics-by-subreddit.png", 
       plot = topics_by_subreddit, 
       width = 8, height = 12)
```

```{r session, include=TRUE, eval=TRUE}
devtools::session_info()
```
