---
title: "Script for using the Reddit API to Collect Subreddit Data"
author: "K. Bret Staudt Willet"
date: "`r Sys.Date()`"
output: html_document
---

## Get set up

This section loads the data and packages and starts to process the data.

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, include=FALSE, eval=TRUE)
library(tidyverse)
library(anytime)
library(lubridate)
library(beepr)

#devtools::install_github("ropenscilabs/roomba")  # <------ currently returns an error and cannot install
#devtools::install_github("jrosen48/roomba")  # this one works; only have to install once
library(roomba)
source("local-functions.R")
```

## Data Collection

### Posts (Preliminary Data Analysis)

```{r, eval=FALSE}
subreddit_posts_teachers0 <- 
  get_posts("Teachers", max_posts = 1000) 
subreddit_posts_teachers <- 
  clean_posts(subreddit_posts_teachers0)
beepr::beep(8)
```

```{r, eval=FALSE}
write_csv(subreddit_posts_teachers, "data/subreddit-posts-teachers-oct2-2021.csv")
```

```{r, message=FALSE}
subreddit_posts_teachers1 <- 
  read_csv("data/subreddit-posts-teachers-oct2-2021.csv") %>% 
  mutate(post_date = floor_date(post_date_time, 'day')) %>%
  select(subreddit, post_id, post_author, post_date, post_date_time,
         post_title, post_text, num_comments, post_score, post_link)
```

```{r, eval=FALSE}
subreddit_posts_teachers1 <-
  subreddit_posts_teachers %>% 
  mutate(post_date = floor_date(post_date_time, 'day'))

earliest_post_teachers <- 
  min(subreddit_posts_teachers1$post_date)
last_post_teachers <- 
  max(subreddit_posts_teachers1$post_date)

subreddit_dates <- 
  subreddit_posts_teachers1 %>% 
  count(post_date)

subreddit_dates
```

Our data collection allowed us to retreive `r nrow(subreddit_posts_teachers1)` posts from r/Teachers, going back to `r earliest_post_teachers`.

### Visualization of Daily Posts by Subreddit

```{r, include=TRUE, message=FALSE, fig.width=8, fig.height=4.5}
ggplot(data = subreddit_dates, mapping = aes(x=post_date, y=n)) +
  geom_point() +
  geom_line() +
  scale_colour_brewer(palette = "Set1") +
  xlab(NULL) +
  ylab("Number of Posts") +
  ggtitle("r/Teachers posts") +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "gray30"),
        panel.grid.minor = element_line(color = "gray90"),
        plot.title=element_text(size=48, family='serif'),
        axis.title=element_text(size=28, family='serif'),
        axis.text=element_text(size=24, family='serif'),
        legend.position='bottom',
        legend.box = 'vertical',
        legend.box.background = element_rect(),
        legend.title=element_text(size=28, family='serif'), 
        legend.text=element_text(size=24, family='serif')
  )
```

```{r, eval=FALSE}
ggsave("output/plot-posts-over-time-oct2.png", width = 8, height = 4.5)
``` 

### Comments (Preliminary Data Analysis)

```{r, eval=FALSE}
subreddit_comments_he <-
  get_comments(subreddit_posts_he) ## This takes a while to run!!!
dim(subreddit_posts_he); dim(subreddit_comments_he)
beepr::beep(8)
```

```{r, eval=FALSE}
write_csv(subreddit_comments_he, "subreddit-comments-he.csv")
```

```{r, eval=FALSE}
subreddit_comments_prof <-
  get_comments(subreddit_posts_prof) ## This takes a while to run!!!
dim(subreddit_posts_prof); dim(subreddit_comments_prof)
beepr::beep(8)
```

```{r, eval=FALSE}
write_csv(subreddit_comments_prof, "subreddit-comments-Prof.csv")
```

```{r, message=FALSE}
subreddit_comments_he <- 
  read_csv("r-highereducation-comments-may2020-sep2020.csv")
subreddit_comments_prof <- 
  read_csv("r-Professors-comments-may2020-sep2020.csv")
```

```{r}
earliest_comment_he <- 
  min(subreddit_comments_he$comment_date_time) %>% date()
last_comment_he <- 
  max(subreddit_comments_he$comment_date_time) %>% date()
earliest_comment_prof <- 
  min(subreddit_comments_prof$comment_date_time) %>% date()
last_comment_prof <- 
  max(subreddit_comments_prof$comment_date_time) %>% date()
```

Our data collection allowed us to retreive `r nrow(subreddit_comments_he1)` comments from r/highereducation, going back to `r earliest_comment_he`, and `r nrow(subreddit_comments_prof1)` comments from r/Professors, going back to `r earliest_comment_prof`.

```{r}
merged_tibble_he <- 
  merge_posts_comments(subreddit_posts_he, subreddit_comments_he)
#nrow(subreddit_posts_he); nrow(subreddit_comments_he)
#length(unique(merged_tibble_he$post_id)); length(unique(merged_tibble_he$comment_id)) - 1 # subtract 1 for NAs
```

```{r}
merged_tibble_prof <- 
  merge_posts_comments(subreddit_posts_prof, subreddit_comments_prof)
#nrow(subreddit_posts_prof); nrow(subreddit_comments_prof)
#length(unique(merged_tibble_prof$post_id)); length(unique(merged_tibble_prof$comment_id)) - 1 # subtract 1 for NAs
```

### Visualization of Daily Comments by Subreddit

```{r}
to_plot_comments_he <-
  subreddit_comments_he %>%
  filter(comment_date_time >= date_start,
         comment_date_time <= date_end) %>%
  pull(comment_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(date = as_date(date),
         subreddit = "r/highereducation")

to_plot_comments_prof <-
  subreddit_comments_prof %>%
  filter(comment_date_time >= date_start,
         comment_date_time <= date_end) %>%
  pull(comment_date_time) %>%
  date() %>%
  table() %>% 
  as_tibble() %>%
  rename(date = ".") %>%
  mutate(date = as_date(date),
         subreddit = "r/Professors")

to_plot_comments <- 
  bind_rows(to_plot_comments_he, to_plot_comments_prof)
```

```{r, include=TRUE, message=FALSE, fig.width=16, fig.height=9}
ggplot(data = to_plot_comments, mapping = aes(x=date, y=n, color=subreddit)) +
  geom_point(size = 5, alpha=.7) +
  scale_color_manual(values = c("#63ACBE", "#EE442F")) + 
  geom_smooth(method='lm', se=FALSE, size=2) +
  xlab(NULL) +
  ylab("Number of Commentss") +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "gray30"),
        panel.grid.minor = element_line(color = "gray90"),
        axis.title=element_text(size=28, family='serif'),
        axis.text=element_text(size=24, family='serif'),
        legend.position='bottom',
        legend.box = 'vertical',
        legend.box.background = element_rect(),
        legend.title=element_text(size=28, family='serif'), 
        legend.text=element_text(size=24, family='serif')
  ) +
  labs(color='Subreddit')
```

```{r, eval=FALSE}
ggsave("plot-comments-over-time.png", width = 16, height = 9)
``` 

### Figure 1. Daily contributions to r/highereducation and r/Professors (2019 vs. 2020)


### Figure 2. Contributors to r/highereducation and r/Professors (2019 vs. 2020)


### Degree of Contribution to r/highereducation and r/Professors (2019 vs. 2020)


### Figure 3. Response Rate in r/highereducation and r/Professors (2019 vs. 2020)


### Figure 4. Thread Lengths in r/highereducation and r/Professors (2019 vs. 2020)




```{r session, include=TRUE, eval=TRUE}
devtools::session_info()
```
